MSB104_assignment1

### 2023-10-04 MSB104_assignment1.qmd
New update

>>>>

```{r}
library(readr)
nama_10r_3gdp_page_linear_csv <- read_csv("nama_10r_3gdp_page_linear.csv.gz", 
    na = "NA", show_col_types = FALSE)
```

```{r}
DE_FI_RO_gdp <- nama_10r_3gdp_page_linear_csv |>
	filter(str_sub
	       (geo, start = 1L, end = 2L) %in% c("DE", "FI", "RO")) |>
	select(year = TIME_PERIOD, geo, gdp = OBS_VALUE)
```
